Global Climate and Atmosphere Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and Spitzer Phase Curve Observations

### 2018-01-07 ms.tex
fussing

\begin{abstract}
	We present thermal phase curve measurements for the hot Jupiter WASP-103b observed with \emph{Hubble}/WFC3 and \emph{Spitzer}/IRAC. The dayside planet-to-star flux is $0.151\pm0.015\%$, $0.446\pm0.38\%$, and $0.569\pm0.014\%$ in bandpasses centered at $1.4$, $3.6$, and $4.5\mu$m, respectively.  The phase curves have large amplitudes and negligible hotspot offsets, indicative of poor heat redistribution to the nightside. We fit the phase variation with a range of climate maps and find they all provide reasonable fits to the data, but have large degeneracies in temperature (up to 1000 K for a given latitude/longitude). The phase-resolved spectra are consistent with blackbodies in the WFC3 bandpass, with effective temperatures ranging from 2000 K on the nightside to 3000 K on the dayside. However, the dayside spectrum has a strong feature in the \Spitzer\ bands, which we attribute to CO emission and a thermal inversion.  The emission feature is not present on the nightside, indicating changing thermal structure with longitude. We retrieved the atmospheric composition with a 1D thermochemical equilibrium model and found the composition is moderately metal-enriched ($\mathrm{[Fe/H]} =  23^{+29}_{-13}\times$ solar), and the carbon-to-oxygen ratio is below 0.9 at $3\,\sigma$ confidence. In contrast to other hot Jupiters, we do not detect significant water absorption, which we attribute to H$_2$O dissociation and additional opacity from H- and TiO/VO.  We compare the phase curves to 3D general circulation models and find that atmospheric drag is required to explain the small hotspot offsets, but that these models overpredict the phase curve amplitude.  We also compare the WASP-103b spectra to brown dwarfs and young directly imaged companions and find they have significantly larger water features, indicating that surface gravity and irradiation environment play an important role in shaping the spectra of hot Jupiters. 
\end{abstract}

>>>>

\begin{abstract}
	We present thermal phase curve measurements for the hot Jupiter WASP-103b observed with \emph{Hubble}/WFC3 and \emph{Spitzer}/IRAC. The dayside planet-to-star flux is $0.151\pm0.015\%$, $0.446\pm0.38\%$, and $0.569\pm0.014\%$ in bandpasses centered at $1.4$, $3.6$, and $4.5\mu$m, respectively.  The phase curves have large amplitudes and negligible hotspot offsets, indicative of poor heat redistribution to the nightside. We fit the phase variation with a range of climate maps and find they all provide reasonable fits to the data, but have large degeneracies in temperature (up to 1000 K for a given latitude/longitude). The phase-resolved spectra are consistent with blackbodies in the WFC3 bandpass, with effective temperatures ranging from 2000 K on the nightside to 3000 K on the dayside. However, the dayside spectrum has a strong feature in the \Spitzer\ bands, which we attribute to CO emission and a thermal inversion.  The emission feature is not present on the nightside, indicating changing thermal structure with longitude. We retrieved the atmospheric composition with a 1D thermochemical equilibrium model and found the composition is moderately metal-enriched ($\mathrm{[Fe/H]} =  23^{+29}_{-13}\times$ solar), and the carbon-to-oxygen ratio is below 0.9 at $3\,\sigma$ confidence. In contrast to other hot Jupiters, we do not detect significant water absorption, which we attribute to partial H$_2$O dissociation and additional opacity from H- and TiO/VO.  We compare the phase curves to 3D general circulation models and find that atmospheric drag is required to explain the small hotspot offsets, but that these models overpredict the phase curve amplitude.  We also compare the WASP-103b spectra to brown dwarfs and young directly imaged companions and find they have significantly larger water features, indicating that surface gravity and irradiation environment play an important role in shaping the spectra of hot Jupiters. 
\end{abstract}
